\documentclass[a4paper,10pt]{article}
\usepackage[T1]{fontenc}
\usepackage[left=0.6in,right=0.6in,top=0.4in,bottom=0.5in]{geometry}
\usepackage[default]{opensans}
\usepackage[none]{hyphenat}
\usepackage{enumitem, hyperref, titlesec, fontawesome5}

\hypersetup{
  colorlinks   = true, %Colours links instead of ugly boxes
  urlcolor     = blue, %Colour for external hyperlinks
  linkcolor    = blue, %Colour of internal links
  citecolor    = red   %Colour of citations
}

\titleformat*{\section}{\large\bfseries}
\titleformat*{\subsection}{\normalsize\bfseries}

\titlespacing*{\section}{0pt}{17pt plus 0pt minus 0pt}{5pt plus 0pt minus 0pt}
\titlespacing*{\subsection}{0pt}{16pt plus 0pt minus 0pt}{0pt plus 0pt minus 0pt}

\pagestyle{empty}

\linespread{1.3}

% Define a custom list for skills with a bold label
\newlist{bulletlist}{itemize}{1}
\setlist[bulletlist,1]{label=$\bullet$,left=0.15in,noitemsep,topsep=0pt}

\begin{document}

\section*{\Large Georgios Adzhygai}

\begin{tabular}{@{} p{0.15em} l @{\hspace{1em}} p{0.1em} l @{}}
    \faEnvelope[regular] & \href{mailto:georgios@ayorgo.com}{georgios@ayorgo.com} & \faLinkedin & \href{https://www.linkedin.com/in/ayorgo}{linkedin.com/in/ayorgo} \\
    \faGithub & \href{https://github.com/ayorgo}{github.com/ayorgo} & \faStackOverflow & \href{https://stackoverflow.com/users/4755520/ayorgo}{stackoverflow.com/users/4755520/ayorgo}
\end{tabular}

\section*{CITIZENSHIP}
Greece, United Kingdom

\section*{EXPERIENCE}

\subsection*{Senior Data Engineer}
Plentific (property management) \\
Nov 2024 - present \\
London, UK \\
Part of a small team of senior engineers.
\begin{bulletlist}
    \item Building dbt models.
    \item Automating data pipelines.
    \item Creating Looker dashboards.
\end{bulletlist}
\textbf{Skills:} Bash, dbt, Docker, Looker, Python, Snowflake, PostgreSQL, Linux

\subsection*{Machine Learning Engineer}
Lyst (e-commerce) \\
Nov 2019 - Jul 2022 \\
London, UK \\
First ML engineer hire, tasked with establishing robust ML infrastructure and processes to bridge the gap between data scientists and software engineers allowing the former to iterate faster on new models and taking the constant troubleshooting burden off of the shoulders of the latter.
\begin{bulletlist}
    \item Established cloud-based ML pipelines from the ground up, facilitating efficient model deployment and integration.
    \item Contributed to the design and development of user engagement prediction models as well as search and recommendation algorithms.
    \item Developed cloud-based command-line tools for rapid experimentation.
    \item Built a data transformation utility to streamline ingestion from multiple data sources.
    \item Designed monitoring dashboards for real-time performance tracking and reporting.
    \item Mentored junior engineers.
\end{bulletlist}
\textbf{Skills:} Looker, Elasticsearch, Docker, Machine Learning, Python, Bash, Recommender Systems, Information Retrieval, Search Engines, MLOps, Metaflow, Snowflake, SQL, Statistics, Linux, Amazon Web Services (AWS), Terraform

\subsection*{Lead Data Scientist}
ETX Capital (financial services) \\
May 2018 - May 2019 \\
London, UK \\
First data science hire, responsible for building DS/ML infrastructure from the ground up and growing the team.
\begin{bulletlist}
    \item Established coding standards and best practices for the data science team, ensuring consistency and quality.
    \item Built and deployed infrastructure to streamline model integration and deployment.
    \item Developed a customer ranking model and deployed it via a RESTful API.
    \item Led and mentored a team of two data scientists.
\end{bulletlist}
\textbf{Skills: }Tableau, Machine Learning, Python, Bash, SQL, MLOps, Statistics, Linux, pandas, NumPy, Scikit-Learn

\subsection*{Software Engineer}
Zopa (fintech) \\
Jun 2015 - Mar 2017 \\
London, UK
\begin{bulletlist}
    \item Developed peer-to-peer lending platform
    \item Designed core platform components
\end{bulletlist}
\textbf{Skills:} SQL, ASP.NET, .NET, C\#

\subsection*{Experienced Engineer}
InsightSoftware.com (financial reporting) \\
Jun 2014 - Feb 2015 \\
London, UK
\begin{bulletlist}
    \item Contributed to server and client ends of the company's bespoke BI system
    \item Fixed and enhanced core SQL generating engine
    \item Developed custom graphics library
\end{bulletlist}
\textbf{Skills:} SQL, .NET, C\#, JavaScript

\subsection*{.NET Developer}
EPAM Systems (banking) \\
Apr 2013 - May 2014 \\
Kyiv, Ukraine
\begin{bulletlist}
    \item Developed corporate banking software
    \item Created data import and processing tool
    \item Set up continuous integration environments
\end{bulletlist}
\textbf{Skills:} SQL, .NET, C\#

\subsection*{.NET Web Developer}
Terrasoft (customer relationship management) \\
Sep 2011 - Mar 2013 \\
Kyiv, Ukraine
\begin{bulletlist}
    \item Developed web-based CRM on both front and back ends
\end{bulletlist}
\textbf{Skills:} SQL, .NET, C\#, JavaScript

\subsection*{Senior System Dev. Consultant}
SimCorp Ukraine LLC (investment management) \\
Feb 2006 - Apr 2011 \\
Kyiv, Ukraine
\begin{bulletlist}
    \item Developed custom investment management system
    \item Built data extraction and analysis utility
\end{bulletlist}
\textbf{Skills:} SQL, Dyalog APL/W

\section*{EDUCATION}
\textbf{MSc, Applied Mathematics} \\
National Technical University of Ukraine "Kyiv Polytechnic Institute" \\
1999 - 2005 \\
Kyiv, Ukraine
\end{document}
